---
title: "3_viz_KGE_boxplots"
author: "Hassan Dahir"
date: "2023-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
####-------------------------------####
source('../fun_0_loadLibrary.R')
####-------------------------------####
library('ggh4x')
```



```{r}
library(ggplot2)
```


```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")  #with grey
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") #with black

data_sampling <- "maas"
model <- "MLR"

outputDir <- paste0('../viz/', data_sampling, "/")
if (!dir.exists(outputDir)) {
  dir.create(outputDir, showWarnings = FALSE, recursive = TRUE)
}

#setup <- c("uncalibrated", 'all_dis','all_dis_meteo', "allpredictors")

setup <- c("average", "pcr_dis", "lis_dis", "wg3_dis", 'all_dis','all_dis_meteo', "allpredictors")

output_folder <- paste0("../", model,"_output/") #RF_output
```


```{r}
#### data preparation ####

#for(subsample in 1:5){

#average discharge
rf.eval.uncalibrated <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                        '/KGE_allpredictors.csv')) %>%
  
  select(.,grdc_no, KGE, KGE_r, KGE_alpha, KGE_beta) %>%
  mutate(.,setup=factor(setup[1]))


#LISFLOOD discharge
rf.eval.pcr.uncalibrated <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                        '/KGE_allpredictors.csv')) %>%
  select(.,grdc_no, KGE_pcr, KGE_r_pcr, KGE_alpha_pcr, KGE_beta_pcr) %>% 
  rename(., KGE=KGE_pcr, KGE_r=KGE_r_pcr, KGE_alpha=KGE_alpha_pcr, KGE_beta=KGE_beta_pcr) %>% 
  mutate(.,setup=factor(setup[2])) 

#LISFLOOD discharge
rf.eval.lis.uncalibrated <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                            '/KGE_allpredictors.csv')) %>%
  select(., grdc_no, KGE_lis, KGE_r_lis, KGE_alpha_lis, KGE_beta_lis) %>% 
  rename(., KGE = KGE_lis, KGE_r = KGE_r_lis, KGE_alpha = KGE_alpha_lis, KGE_beta = KGE_beta_lis) %>% 
  mutate(., setup = factor(setup[3])) 


#Watergap3 discharge
rf.eval.wg3.uncalibrated <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                            '/KGE_allpredictors.csv')) %>%
  select(., grdc_no, KGE_wg3, KGE_r_wg3, KGE_alpha_wg3, KGE_beta_wg3) %>% 
    rename(., KGE = KGE_wg3, KGE_r = KGE_r_wg3, KGE_alpha = KGE_alpha_wg3, KGE_beta = KGE_beta_wg3) %>% 
    mutate(., setup = factor(setup[4]))


#read all_dis of different models
rf.eval.all_dis <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                         '/KGE_all_dis.csv')) %>% 
  select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
  rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>% 
  mutate(.,setup=factor(setup[5])) 

#read pcr + meteo
rf.eval.all.dis.meteo <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                         '/KGE_all_dis_meteo.csv')) %>% 
  select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
  rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>% 
  mutate(.,setup=factor(setup[6])) 

#read pcr + meteo  + pcr statevariables
rf.eval.allpredictors <- read.csv(paste0(output_folder, 'validate/',data_sampling,
                                         '/KGE_allpredictors.csv')) %>% 
  select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
  rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>% 
  mutate(.,setup=factor(setup[7])) 


#put together in one list
subsample_KGE <- rbind(rf.eval.uncalibrated, rf.eval.pcr.uncalibrated, rf.eval.lis.uncalibrated, rf.eval.wg3.uncalibrated, rf.eval.all_dis, rf.eval.all.dis.meteo, rf.eval.allpredictors)



```






```{r}
allData <- 
  subsample_KGE 

  #do.call(rbind, subsample_KGE_list)
#allDataCum <- allData %>% mutate(subsample='Cumulative')
#allData <- rbind(allData,allDataCum)


plotData <- allData %>% 

  pivot_longer(KGE:KGE_beta, names_to = "KGE_component", 
                                     values_to = "value") %>% 
  mutate(setup = factor(setup, levels=  c("average", "pcr_dis", "lis_dis", "wg3_dis", 'all_dis','all_dis_meteo', "allpredictors"))) %>%
  mutate(KGE_component = fct_relevel(KGE_component, 'KGE','KGE_r','KGE_alpha','KGE_beta'))
```


```{r}
plotData
```


```{r}
KGE_data <-
  plotData %>% 
  filter(., KGE_component == "KGE") %>% 
  group_by(setup) %>%
  
  summarize(median_value = median(value)) 
  #pivot_wider(names_from = subsample, values_from = median_value)

KGE_data
```


```{r}
filename <- paste0("median_KGE_", data_sampling, ".csv")

# Save the data frame as a CSV file
write.csv(KGE_data, file = paste0(outputDir, filename), row.names = FALSE)
```







```{r}
#### plot boxplots ####
KGE_boxplot <- 

  ggplot(plotData , mapping = aes(setup, value, fill=setup))+
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  
  facet_grid(vars(KGE_component), scales='free_y', switch='y')+
  labs(title = paste0("RF KGE ", data_sampling, "\n"))+
  scale_fill_manual(values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F8766D", "#00BFC4", "#7CAE00")) +
  theme(plot.title = element_text(hjust=0.5, size=16),
        axis.title=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y= element_text(size=12),
        legend.position = 'bottom',
        legend.title=element_blank(),
        legend.key.size = unit(1, 'cm'),
        legend.text = element_text(size=14),
        strip.text = element_text(size=12))+
  facetted_pos_scales(y = list(
    KGE_component == "KGE" ~ scale_y_continuous(position='right', limits = c(-4, 1)),
    KGE_component == "KGE_r" ~ scale_y_continuous(position='right', limits = c(0, 1)),
    KGE_component == "KGE_alpha" ~ scale_y_continuous(position='right', limits = c(-0.5,5)),
    KGE_component == "KGE_beta" ~ scale_y_continuous(position='right', limits = c(-0.5,5.5))))
KGE_boxplot
```

```{r}
plotData
```



```{r}
KGE_boxplot <- 
  plotData %>% 
  #filter(., subsample=="Cumulative") %>% 

  filter(., KGE_component %in% c("KGE")) %>% #, "KGE_r", "KGE_alpha", "KGE_beta"
  ggplot(. , mapping = aes(setup, value, fill=setup))+
  geom_boxplot(outlier.shape = NA) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  facet_grid(vars(KGE_component),  scales='free_y', switch='y')+
  labs(title = paste0("Subsampling ", data_sampling, " ", model))+
  scale_fill_manual(values=c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F8766D", "#00BFC4", "#7CAE00"))+
  theme(plot.title = element_text(hjust=0.5, size=16),
        axis.title=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.y= element_text(size=12),
        legend.position = 'bottom',
        legend.title=element_blank(),
        legend.key.size = unit(1, 'cm'),
        legend.text = element_text(size=14),
        strip.text = element_text(size=12))+
  facetted_pos_scales(y = list(
    KGE_component == "KGE" ~ scale_y_continuous(position='right', limits = c(-1, 1))))
    #KGE_component == "KGE_r" ~ scale_y_continuous(position='right', limits = c(0, 1)),
    #KGE_component == "KGE_alpha" ~ scale_y_continuous(position='right', limits = c(-0.5,5)),
    #KGE_component == "KGE_beta" ~ scale_y_continuous(position='right', limits = c(-0.5,5.5))))
KGE_boxplot
```




```{r}
#Save fig

ggsave(paste0(outputDir,'KGE_boxplots_', model, data_sampling,  '.png'), KGE_boxplot, height=10, width=10, units='in', dpi=600)
```



```{r}
KGE_data <-
  plotData %>% 
  filter(., KGE_component == "KGE") %>% 
  group_by(setup) %>%
  #filter(., subsample=="Cumulative") %>% 

  summarize(median_value = median(value))
  #pivot_wider(names_from = subsample, values_from = median_value)

KGE_data
```


```{r}
filename <- paste0('median_KGE_', model, '.csv')

# Save the data frame as a CSV file            
write.csv(KGE_data, file = paste0(outputDir, filename), row.names = FALSE)
```






```{r}
#### some stats (paper section 3.3.) ####

setup <- c("uncalibrated", 'all_dis','all_dis_meteo', "allpredictors")


uncalibratedCum <- allDataCum %>% filter(setup=='uncalibrated')
Discharge_onlyCum <- allDataCum %>% filter(setup=='pcr_predicted')

print("-------------KGE-------------")
mean(summary(uncalibratedCum$KGE))
summary(Discharge_onlyCum$KGE)

print("-------------KGE_r-------------")
summary(uncalibratedCum$KGE_r)
summary(Discharge_onlyCum$KGE_r)


print("-------------KGE_alpha-------------")
summary(uncalibratedCum$KGE_alpha)
summary(Discharge_onlyCum$KGE_alpha)

print("-------------KGE_beta-------------")
summary(uncalibratedCum$KGE_beta)
summary(Discharge_onlyCum$KGE_beta)

```


```{r}
calculate_and_print_summaries <- function(allDataCum, setup) {
  setupCum1 <- allDataCum %>% filter(setup == setup)
  
  print("-------------KGE-------------")
  print(mean(summary(setupCum1$KGE)))
  print(summary(setupCum1$KGE))
  
  print("-------------KGE_r-------------")
  print(summary(setupCum1$KGE_r))
  
  print("-------------KGE_alpha-------------")
  print(summary(setupCum1$KGE_alpha))
  
  print("-------------KGE_beta-------------")
  print(summary(setupCum1$KGE_beta))
  
  return(setupCum1)
}

setup <- c("uncalibrated", 'all_dis','all_dis_meteo', "allpredictors")
uncalibratedCum <- calculate_and_print_summaries(allDataCum, setup[1])
```


```{r}
setup <- c("uncalibrated", 'all_dis','all_dis_meteo', "allpredictors")
AllpredictursCum <- calculate_and_print_summaries(allDataCum, setup[4])
```


```{r}
AllpredictursCum
```







```{r}
# Calculate mean values
uncalibrated_mean <- mean(uncalibratedCum$KGE)
discharge_only_mean <- mean(Discharge_onlyCum$KGE)
uncalibrated_r_mean <- mean(uncalibratedCum$KGE_r)
discharge_only_r_mean <- mean(Discharge_onlyCum$KGE_r)
uncalibrated_alpha_mean <- mean(uncalibratedCum$KGE_alpha)
discharge_only_alpha_mean <- mean(Discharge_onlyCum$KGE_alpha)
uncalibrated_beta_mean <- mean(uncalibratedCum$KGE_beta)
discharge_only_beta_mean <- mean(Discharge_onlyCum$KGE_beta)

# Create a dataframe
data_stats <- data.frame(
  Metric = c("KGE", "KGE_r", "KGE_alpha", "KGE_beta"),
  Uncalibrated = c(uncalibrated_mean, uncalibrated_r_mean, uncalibrated_alpha_mean, uncalibrated_beta_mean),
  Discharge_only = c(discharge_only_mean, discharge_only_r_mean, discharge_only_alpha_mean, discharge_only_beta_mean)
)

# Print the dataframe
data_stats

```









  #read pcr_discharge_only
  rf.eval.pcr_discharge_only <- read.csv(paste0('../RF/3_validate/subsample_', subsample,
                                           '/KGE_pcr_dis.csv')) %>% 
    select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
    rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>%
    mutate(.,setup=factor(setup[2])) %>% 
    mutate(.,subsample=factor(subsample)) 
  
  
  
   #read pcr + meteo
  rf.eval.pcr_meteo <- read.csv(paste0('../RF/3_validate/subsample_', subsample,
                                           '/KGE_pcr_dis_meteo.csv')) %>% 
    select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
    rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>% 
    mutate(.,setup=factor(setup[3])) %>% 
    mutate(.,subsample=factor(subsample)) 
  
  #read pcr + meteo  + pcr statevariables
  rf.eval.pcr_allpredictors <- read.csv(paste0('../RF/3_validate/subsample_', subsample,
                                           '/KGE_pcr_allpredictors.csv')) %>% 
    select(.,grdc_no, KGE_corrected, KGE_r_corrected, KGE_alpha_corrected, KGE_beta_corrected) %>% 
    rename(., KGE=KGE_corrected, KGE_r=KGE_r_corrected, KGE_alpha=KGE_alpha_corrected, KGE_beta=KGE_beta_corrected) %>% 
    mutate(.,setup=factor(setup[4])) %>% 
    mutate(.,subsample=factor(subsample))

